---
title: "STAT 892 Group Presentation"
author: "Tyler Wiederich, Wyatt McLeod, Aaron Schram, Neetu Regmi, Madison King"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

## Cross Validation of Models

```{r, echo=FALSE}
five_fold = function(x, y, threshold = 0.5, epsilon = 1e-14){
  require(pROC)
  
  #Location of predicted values from models
  yhat_l = numeric()
  yhat_p = numeric()
  yhat_c = numeric()
  
  for(i in 1:5){
    
    #Split data
    y_id = rep(1:5, each = 100)
    ytrain = y[y_id != i]
    ytest = y[y_id == i]
    
    xtrain = as.data.frame(x[y_id != i, -1])
    xtest = as.data.frame(x[y_id == i, -1])
    
    
    
    #Fitting the three models
    fit_logit = glm(ytrain ~ ., family = binomial(link = 'logit'),
                epsilon = epsilon, data = xtrain)
    fit_probit = glm(ytrain ~ ., family = binomial(link = 'probit'),
                epsilon = epsilon, data = xtrain)
    fit_cloglog = glm(ytrain ~ ., family = binomial(link = 'cloglog'),
                epsilon = epsilon, data = xtrain)

    
    
    #Predicted probabilities
    pihat_l = predict.glm(fit_logit, newdata = xtest, type = 'response')
    pihat_p = predict.glm(fit_probit, newdata = xtest, type = 'response')
    pihat_c = predict.glm(fit_cloglog, newdata = xtest, type = 'response')
    
    
    
    #Predicted y value with threshold of 0.5
    temp_yhat_l = ifelse(pihat_l >= threshold, 1, 0)
    temp_yhat_p = ifelse(pihat_p >= threshold, 1, 0)
    temp_yhat_c = ifelse(pihat_c >= threshold, 1, 0)
    
    yhat_l = append(yhat_l, temp_yhat_l)
    yhat_p = append(yhat_p, temp_yhat_p)
    yhat_c = append(yhat_c, temp_yhat_c)
    
  }
  
  #Confusion matrix
    cmatrix_l = table(yhat_l, y)
    cmatrix_p = table(yhat_p, y)
    cmatrix_c = table(yhat_c, y)
    
  #ROC
    roc_l <- roc(y ~ predict.glm(glm(y~x, family = binomial(link = 'logit')), type ='response'), plot = F, print.auc = T) |> suppressMessages()
    roc_p <- roc(y ~ predict.glm(glm(y~x, family = binomial(link = 'probit')), type ='response'), plot = F, print.auc = T) |> suppressMessages()
    roc_c <- roc(y ~ predict.glm(glm(y~x, family = binomial(link = 'cloglog')), type ='response'), plot = F, print.auc = T) |> suppressMessages()
    
    
    
    res = list(logit = list(confusion_matrix = cmatrix_l, auc = as.numeric(roc_l$auc)),
               probit = list(confusion_matrix = cmatrix_p, auc = as.numeric(roc_p$auc)),
               cloglog = list(confusion_matrix = cmatrix_c, auc = as.numeric(roc_c$auc)))
    return(res)
}
```

For the comparison of models, we are using `five_fold()`. This function will perform the following:

-   Split data into five different training-test sets
-   Fit `glm()` with logit, probit, and cloglog links
-   Create a confusion matrix using the predicted results for each link
-   Produce ROC across the entire dataset (no training-test sets) for each link

## True Logistic Model

$$\pi = \frac{e^{x\beta}}{1+e^{x\beta}}$$

```{r message=FALSE, warning=FALSE}
set.seed(5326)
n = 500; p = 5
x = cbind(1, t(replicate(n = n, expr = rnorm(n = p))))
beta = matrix(c(1.5, 3.7, -1.5, 4, -0.8, -4.2),
              ncol = 1)
xb = x %*% beta

pi = exp(xb)/(1+exp(xb))
y_l = rbinom(n = n, size = 1, prob = pi)
res_logit = five_fold(x, y_l)
```

## True Probit Model

$$\pi=\Phi(x\beta)$$

```{r, warning=FALSE}
set.seed(5326)
n = 500; p = 5
x = cbind(1, t(replicate(n = n, expr = rnorm(n = p))))
beta = matrix(c(1.5, 3.7, -1.5, 4, -0.8, -4.2),
              ncol = 1)
xb = x %*% beta

pi = pnorm(xb)
y_p = rbinom(n = n, size = 1, prob = pi)
res_probit = five_fold(x, y_p)
```

## True Complimentary Log Log

$$\pi=1-e^{-e^{x\beta}}$$

```{r, warning=FALSE}
set.seed(5326)
n = 500; p = 5
x = cbind(1, t(replicate(n = n, expr = rnorm(n = p))))
beta = matrix(c(1.5, 3.7, -1.5, 4, -0.8, -4.2),
              ncol = 1)
xb = x %*% beta

pi = 1-exp(-exp(xb))
y_c = rbinom(n = n, size = 1, prob = pi)
res_cloglog = five_fold(x, y_c)
```



## Summary of Results

```{r, echo=FALSE}
dat = rbind(
  cbind(res_logit[[1]][[1]], res_probit[[1]][[1]], res_cloglog[[1]][[1]]),
  cbind(res_logit[[2]][[1]], res_probit[[2]][[1]], res_cloglog[[2]][[1]]),
  cbind(res_logit[[3]][[1]], res_probit[[3]][[1]], res_cloglog[[3]][[1]])
)

library(kableExtra)
kable(dat, align = 'c') %>% 
  add_header_above(c('Fitted Model' = 1, 'Logit' = 2, 'Probit' = 2, 'C-Log-Log' = 2)) %>% 
  add_header_above(c(' ' = 1, 'True Model' = 6)) %>% 
  pack_rows(index = c('Logit' = 2, 'Probit' = 2, 'C-Log-Log' = 2)) %>% 
  kable_styling(font_size = 16)
```

## ROC Plots

```{r message=FALSE, warning=FALSE, echo=FALSE, results='hide'}
par(mfrow = c(3,3))

#Fitted Logit
roc(y_l ~ predict.glm(glm(y_l~x, family = binomial(link = 'logit')), type ='response'), plot = T, print.auc = T, main = 'True Logit\nFitted Logit') |> suppressMessages()

roc(y_p ~ predict.glm(glm(y_p~x, family = binomial(link = 'logit')), type ='response'), plot = T, print.auc = T, main = 'True Probit\nFitted Logit') |> suppressMessages()

roc(y_c ~ predict.glm(glm(y_c~x, family = binomial(link = 'logit')), type ='response'), plot = T, print.auc = T, main = 'True C-log-log\nFitted Logit') |> suppressMessages()


#Fitted Probit
roc(y_l ~ predict.glm(glm(y_l~x, family = binomial(link = 'probit')), type ='response'), plot = T, print.auc = T, main = 'True Logit\nFitted Logit') |> suppressMessages()

roc(y_p ~ predict.glm(glm(y_p~x, family = binomial(link = 'probit')), type ='response'), plot = T, print.auc = T, main = 'True Probit\nFitted Probit') |> suppressMessages()

roc(y_c ~ predict.glm(glm(y_c~x, family = binomial(link = 'probit')), type ='response'), plot = T, print.auc = T, main = 'True C-Log-Log\nFitted Probit') |> suppressMessages()


#Fitted C-log-log
roc(y_l ~ predict.glm(glm(y_l~x, family = binomial(link = 'cloglog')), type ='response'), plot = T, print.auc = T, main = 'True Logit\nFitted Logit') |> suppressMessages()

roc(y_p ~ predict.glm(glm(y_p~x, family = binomial(link = 'cloglog')), type ='response'), plot = T, print.auc = T, main = 'True Probit\nFitted C-Log-Log') |> suppressMessages()

roc(y_c ~ predict.glm(glm(y_c~x, family = binomial(link = 'cloglog')), type ='response'), plot = T, print.auc = T, main = 'True C-Log-Log\nFitted C-Log-Log') |> suppressMessages()
```


## AUC Values

```{r, echo=FALSE}
rc = expand.grid(cols = c('Logit', 'Probit', 'C-Log-Log'), 
                 rows = c('Logit', 'Probit', 'C-Log-Log'))

vals = as.numeric(c(res_logit$logit[2], res_probit$logit[2], res_cloglog$logit[2],
             res_logit$probit[2], res_probit$probit[2], res_cloglog$probit[2],
             res_logit$cloglog[2], res_probit$cloglog[2], res_cloglog$cloglog[2]))

auc = cbind(rc, vals)
library(ggplot2)
ggplot(mapping = aes(x = auc$cols, y = auc$rows,
                     fill = auc$vals)) +
  geom_tile() +
  geom_label(mapping = aes(label = round(auc$vals, 3))) +
  labs(title = 'AUC', x = 'True Model', y = 'Fitted Model', fill = 'AUC') +
  coord_equal() +
  scale_y_discrete(limits = rev) +
  theme_bw() +
  theme(axis.title.y = element_text(angle = 0, vjust = 0.5),
        plot.title = element_text(hjust = 0.5))

```

